|

### 2024-05-28 rmds/figures.Rmd
revisions

Figure 3. Accuracy (per cent absolute error) in parameter estimates of $\hat{P_{Max}}$ for 3PLF methods. Large sample sizes were needed to accurately estimate $\hat{P_{Max}}$ and accuracy decreased as the duration of the reproductive cycle increased. Each point reflects a mean value from 300 simulated data sets.\
\
\newpage

@@

Figure 4. Confidence interval coverage for $\hat{L'_{50}}$ for 3PLF methods (high selectivity scenarios). Figure shows the percentage of simulations (n = 300) where the true parameter value fell within the 50% bootstrap confidence interval.\
\
\newpage

>>>>

Figure 3. Accuracy (per cent absolute error) in parameter estimates of $\hat{P_{Max}}$ for 3PLF methods. Large sample sizes were needed to accurately estimate $\hat{P_{Max}}$ and accuracy decreased as the duration of the reproductive cycle increased. Each point reflects a mean value from 300 simulated data sets. Point size denotes mean number of females in maternal condition at a given sample size. \
\
\newpage

@@

Figure 4. Confidence interval coverage for $\hat{L'_{50}}$ for 3PLF methods (high selectivity scenarios). Figure shows the percentage of simulations (n = 300) where the true parameter value fell within the 50% bootstrap confidence interval. Point size denotes mean number of females in maternal condition at a given sample size. \
\
\newpage

### 2024-05-28 rmds/manuscript.Rmd
revisions

For the 3PLF methods, parameter estimates tended to be biased high at lower sample sizes (Figure S2, Figure S3). In some scenarios, particularly with sample sizes $\leq$ 250, fixing the asymptote was effective at reducing bias, although for larger sample sizes neither method was clearly preferable (Figure S2, Figure S3). The accuracy of parameter estimates varied considerably across different combinations of variables used in the simulation and among parameters (Figure S4, Figure S5). Again, in some scenarios with smaller sample sizes $\leq$ 250, fixing the asymptote improved accuracy with the 3PLF methods, although at larger sample sizes better accuracy was achieved by estimating $P_{Max}$ (Figure 3). Overall, $P_{Max}$ was comparatively more challenging to estimate accurately than $L'_{50}$ (Figure S4, Figure S5).

@@

Differences in life history and gear selectivity played an important role in the ability to obtain accurate and unbiased maternity parameters. Certain combinations of variables in the simulated data resulted in fewer females in maternal or immature condition, making parameter estimation difficult (Figure S8, Figure S9). This was particularly the case for $P_{Max}$ which required a relatively high maternal sample size to enable accurate parameter estimation (Figure 5). These effects were not necessarily consistent between species and seemed to reflect differences in the underlying population length structure. For example, in biennial low selectivity scenarios for gummy sharks \~60% of individuals were immature compared to \~50% in the corresponding scenarios for school sharks (Figure S9).

@@

Relatively few reproductive biology studies have used maternity functions to model maternal reproductive output in chondrichthyan fishes. Where they have been employed the approach has typically been to use a three parameter logistic function with a fixed, user-defined value for the upper asymptote, $P_{Max}$. Here we show that it is feasible to estimate $P_{Max}$ from maternal data, in turn enabling statistical inferences on reproductive periodicity. Applying 3PLF models with estimated and fixed values of $P_{Max}$ to simulated data showed that accuracy, bias, and confidence interval coverage often improved when $P_{Max}$ was estimated. Using a fixed value for $P_{Max}$ in some cases resulted in lower bias at low sample sizes. This study also demonstrated that recruitment can be overestimated when maturity data were used to approximate maternal data and inaccurate if $P_{Max}$ was ignored when estimating maternity parameters. Based on these findings we outline considerations for practitioners using these methods and illustrate how they can provide novel insights into reproductive biology. We conclude by discussing the advantages of adopting this approach to quantifying maternal reproductive output and future directions.

@@

Using simulated data to compare the relative performance of the 3PLF-estimated and 3PLF-fixed methods subject to a range of variables showed that it was feasible to estimate $P_{Max}$ from data, but also identified situations where it may be preferable to fix $P_{Max}$. Providing clear guidelines on this is difficult

In most scenarios, sample sizes of upward of 100 maternal females were needed for the 3PLF-estimated method to consistently exceed the performance of the 3PLF-fixed method. 
At sample sizes below this it is therefore advisable to fix $P_{Max}$. Larger sample sizes are necessary before attempting to estimate $P_{Max}$ in species with a triennial or longer reproductive cycle, due to the decline in the performance of the 3PLF-estimated method as $P_{Max}$ decreases.

While the estimation of maternity parameters in most simulations was possible, it was difficult to do so accurately. Outcomes of the simulation study suggested that samples sizes of $\geq500$ would be needed to estimate $P_{Max}$ with \<10% MARE for a triennially reproducing species. This is a much larger error than is achievable from conventional logistic maturity analysis [@roa_estimation_1999]. In the case of the gummy shark this inaccuracy led to the 2PLF-maturity method performing comparably or better than the 3PLF methods in ultimately quantifying $R_0$. Relatively wide confidence intervals were also obtained for $P_{Max}$ in the empirical analysis for sandbar sharks, even with a sample size of \> 1000. A similar sample size was used by Colonello *et al*. [-@colonello_reproductive_2016] to estimate plausible values of $P_{Max}$ and maternity parameters for south Atlantic spiny dogfish. These results suggest that data requirements of the 3PLF analyses may be prohibitively large for many chondrichthyans and therefore best suited to use on commercially captured species where large sample sizes can be obtained [@oddone_size_2010; @tribuzio_life_2012].

In light of the data requirements suggested by this study, placing a penalty function on $P_{Max}$ or using a the use of a prior distribution

For some species, and data on pregnant females are particularly sparse, the current practice of using maturity parameters as a proxy for maternity parameters will likely still be the only option for numerous data-poor chondrichthyans. From this perspective, the outperformance of the 3PLF-methods by the 2PLF-methods for the gummy shark in several simulations is encouraging. However, the extent to which maturity parameters can provide a good approximation of maternity parameters may be species-specific, depending on how close $L_{50}$ is to $L'_{50}$. While several studies have shown these parameters to be similar [@walker_spatial_2007; @soto-lopez_reproductive_2018], $L'_{50}$ is more frequently shifted to the right of $L_{50}$ [@braccini_determining_2006; @palacios-hernandez_temporal_2020; @montealegre-quijano_sexual_2014; @colonello_reproductive_2016], and this length difference can equate to one or more years. For example, Harry et al. [-@harry_age_2013] found both spot-tail shark, *C. sorrah*, and Australian blacktip shark, *C. tilstoni*, began reproducing the year after reaching sexual maturity. Similarly, Fujinami et al. [-@fujinami_reproductive_2017] found $A'_{50}$ to be 1.4 years older than $A_{50}$ in blue sharks.

@@

Another approach to overcoming the

The success of any analysis using the 3PLF-fixed or 2PLF-maturity methods, as implemented here, ultimately depends on the analyst choosing a suitable value for $P_{Max}$. In this study, the value for $P_{Max}$ used in the fixed analyses was chosen based on the proportion of maternal females observed in the simulated data. The potential to introduce a greater level of bias in the analysis through the incorrect selection of $P_{Max}$ should also be considered if using this approach.

>>>>

For the 3PLF methods, parameter estimates tended to be biased high at lower sample sizes (Figure S2, Figure S3). In some scenarios, particularly with sample sizes $\leq$ 250, fixing the asymptote was effective at reducing bias, although for larger sample sizes neither method was clearly preferable (Figure S2, Figure S3). The accuracy of parameter estimates varied considerably across different combinations of variables used and among parameters (Figure S4, Figure S5). Again, in some scenarios with smaller sample sizes $\leq$ 250, fixing the asymptote improved accuracy with the 3PLF methods, although at larger sample sizes better accuracy was achieved by estimating $P_{Max}$ (Figure 3). Overall, $P_{Max}$ was comparatively more challenging to estimate accurately than $L'_{50}$ (Figure S4, Figure S5).

@@

Differences in life history and gear selectivity played an important role in the ability to obtain accurate and unbiased maternity parameters. Certain combinations of variables in the simulated data resulted in few females in maternal or immature condition, making parameter estimation difficult (Figure S8, Figure S9). This was particularly the case for $P_{Max}$ which required a relatively high maternal sample size to enable accurate parameter estimation (Figure 5). These effects were not necessarily consistent between species and seemed to reflect differences in the underlying population length structure. For example, in biennial low selectivity scenarios for gummy sharks \~60% of individuals were immature compared to \~50% in the corresponding scenarios for school sharks (Figure S9).

@@

Relatively few reproductive biology studies have used maternity functions to model maternal reproductive output in chondrichthyan fishes. Where they have been employed the approach has typically been to use a three parameter logistic function with a fixed, user-defined value for the upper asymptote, $P_{Max}$. Here we show that it is feasible to estimate $P_{Max}$ from maternal data, in turn enabling statistical inferences on reproductive periodicity. Applying 3PLF models with estimated and fixed values of $P_{Max}$ to simulated data showed that accuracy, bias, and confidence interval coverage often improved when $P_{Max}$ was estimated. Using a fixed value for $P_{Max}$ in some cases resulted in lower bias at low sample sizes. Overall, relatively large sample sizes were needed to estimated $P_{Max}$ accurately, particularly in species with longer reproductive cyles. This study also demonstrated that recruitment can be overestimated when maturity data were used to approximate maternal data and inaccurate if $P_{Max}$ was ignored when estimating maternity parameters. Based on these findings we outline considerations for practitioners using these methods and illustrate how they can provide novel insights into reproductive biology. We conclude by discussing the advantages of adopting this approach to quantifying maternal reproductive output and future directions.

@@

Using simulated data to compare the relative performance of the 3PLF-estimated and 3PLF-fixed methods subject to a range of variables showed that it was feasible to estimate $P_{Max}$ from data, but also identified situations where it may be preferable to fix $P_{Max}$. Providing clear guidelines on this is difficult as model performance was influenced by life history traits and gear selectivity. In most scenarios, sample sizes of at least 100 were needed for the 3PLF-estimated method to approach or exceed the performance of the 3PLF-fixed method. At sample sizes below this it is therefore advisable to fix $P_{Max}$. Larger sample sizes are necessary before attempting to estimate $P_{Max}$ in species with a triennial or longer reproductive cycle, due to the decline in the performance of the 3PLF-estimated method as $P_{Max}$ decreases.

While the estimation of maternity parameters in most simulations was possible, it was difficult to do so accurately. Outcomes of the simulation study showed that for non-annual reproductive cycles $\geq100$ and $\geq200$ maternal females were typically needed to estimate $P_{Max}$ with \<10% MARE for school and gummy sharks, respectively. This is a much larger error than is achievable from conventional logistic maturity analysis [@roa_estimation_1999]. In the case of the gummy shark this inaccuracy led to the 2PLF-maturity method performing comparably or better than the 3PLF methods in ultimately quantifying $R_0$. Relatively wide confidence intervals were also obtained for $P_{Max}$ in the empirical analysis for sandbar sharks, even with a total sample size of \> 1000 females, of which 206 were in maternal condition. A similar sample size was used by Colonello *et al*. [-@colonello_reproductive_2016] to estimate plausible values of $P_{Max}$ and maternity parameters for south Atlantic spiny dogfish.

These results suggest that data requirements of the 3PLF analyses may be prohibitively large for many chondrichthyans and therefore best suited to use on commercially captured species where large sample sizes can be obtained [@oddone_size_2010; @tribuzio_life_2012]. For smaller samples sizes, placing a prior or penalty on $P_{Max}$ may also help overcome issues of parameter inaccuracy, enabling existing information about reproductive periodicity to be incorporated from other populations or closely-related species [@10.1371/journal.pone.0246734]. Information on length at maturity, which is likely to be relatively easier to estimate, may also be informative in the development of priors, with $L_{50}$ effectively providing a lower bound for $L'_{50}$.

For particularly data-poor species, or where data on pregnant females are sparse or unattainable, the current practice of using maturity parameters as a proxy for maternity parameters will likely still be the only option. From this perspective, the outperformance of the 3PLF-methods by the 2PLF-methods for the gummy shark in several simulations is encouraging. However, the extent to which maturity parameters can provide a good approximation of maternity parameters may be species-specific, depending on how close $L_{50}$ is to $L'_{50}$. While several studies have shown these parameters to be similar [@walker_spatial_2007; @soto-lopez_reproductive_2018], $L'_{50}$ is more frequently shifted to the right of $L_{50}$ [@braccini_determining_2006; @palacios-hernandez_temporal_2020; @montealegre-quijano_sexual_2014; @colonello_reproductive_2016], and this length difference can equate to one or more years. For example, Harry et al. [-@harry_age_2013] found both spot-tail shark, *C. sorrah*, and Australian blacktip shark, *C. tilstoni*, began reproducing the year after reaching sexual maturity. Similarly, Fujinami et al. [-@fujinami_reproductive_2017] found $A'_{50}$ to be 1.4 years older than $A_{50}$ in blue sharks.

@@
